Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-04-29 code-tests.tex
Oh just kidding, I forgot to edit the code comparison section (4.1.2).  Onward and upward, to the test problem section!

Over the course of its existence, \enzo\ has been involved in several
comparisons with other astrophysical codes used for self-gravitating
fluid dynamics.  In general, \enzo\ behaves in a manner similar to other
grid-based (and particularly AMR-based) codes, as we will summarize below.

\enzo\ has been involved in several cosmological code comparisons,
including the Santa Barbara Cluster code comparison project
\citep{SantaBarbara}, a large comparison of N-body simulations
\citep{2008CS&D....1a5003H}, as well as several direct comparisons
between \enzo\ and the GADGET SPH code under a variety of
circumstances, including N-body and adiabatic hydrodynamics
\citep{2005ApJS..160....1O,2005MNRAS.364..909V, 2011MNRAS.418..960V}
and simulations of the Lyman-alpha forest \citep{2007MNRAS.374..196R}.
The \enzo\ code typically has a more difficult time resolving
small-scale self-gravitating structures (for an equivalent dark matter
particle count and nominally equivalent force resolution), but does
comparably well as a tree-based code for larger structure, and is
typically superior in terms of resolving fluid features due to its
higher-order (and artificial viscosity-free) hydrodynamics solver.
When examining classical test cases such as the Santa Barbara
project \citep{SantaBarbara}, \enzo\ forms galaxy clusters with very similar density,
temperature, and entropy profiles to other grid-based codes that use
Godunov-type hydro methods, which
systematically differ from particle-based codes using SPH.  Similarly,
in galaxy cluster simulations that look specifically at the properties
of cosmological shocks \citep[e.g.][]{2011MNRAS.418..960V}, \enzo\
produces results that are similar to other high-order grid-based
hydrodynamics codes, and far superior behavior of \enzo\ in
low-density regions when compared to a particle-based code.  In tests
of the Lyman-alpha forest that include radiative cooling and a uniform
metagalactic ultraviolet background, \enzo\ and Gadget provide results
on metrics such as the matter power spectrum that are comparable to
within 5\% \citep{2007MNRAS.374..196R}.

Several comparisons have been made that focus specifically on
hydrodynamics solvers.  In particular, the work of
\citet{2007MNRAS.380..963A} and \citet{Tasker2008} perform
head-to-head comparisons between several grid- and particle-based
codes for a variety of test problems (including shocked gas clouds,
self-gravitating, translating clouds, and Sedov-Taylor explosions),
and show that \enzo\ is comparable or superior in behavior to the
other grid-based hydrodynamics codes involved in the comparison, and
provide useful information on whether an AMR code such as \enzo\
experiences challenges.  More specific comparisons, including one
specifically testing the linear and nonlinear growth of the
Kelvin-Helmholz instability \citep{2012ApJS..201...18M} and one more
broadly examining Galilean invariance in grid-based codes
\citep{2010MNRAS.401.2463R} show that \enzo, and in particular its
implementation of the Piecewise Parabolic Method hydrodynamics solver,
converge to the correct solution as expected, and generally provide
less diffusive solutions than lower-order codes, including those that
use artificial viscosity.  Finally, two code comparison projects have
been undertaken to examine turbulence in hydro codes -- one studied
the behavior of decaying isothermal supersonic turbulence
\citep{2009A&A...508..541K}, and the other looked at supersonic
magnetohydrodynamical turbulence \citep{2011ApJ...737...13K}.  Both
included the \enzo\ code, with the former testing the PPM
hydrodynamics and the latter the constrained transport MHD
implementation.  In both cases, \enzo\ performed similarly to other
grid-based codes that use Godunov-based fluid solvers, and typically
had better effective resolution than particle-based codes using the
same number of particles as the \enzo\ simulation used grid cells.

Three other comparisons between portions of the \enzo\ code and other
simulation tools have been performed in recent years.  The
flux-limited diffusion radiation transport scheme was measured against
several test problems by \citet{IlievEtAl2009}, producing results that
are similar to both expected results and other methods, although there
are some minor differences (although all codes in the study exhibited
differences from the majority of other codes on at least a subset of
the tests).  \citet{2011ApJ...726...55T} shows the result of varied
reaction rate coefficients for the formation of molecular hydrogen via
the 3-body process in both the \enzo\ and Gadget-2 codes.  Similar
trends were visible in both the \enzo\ and Gadget simulations, though
at a nominally equivalent resolution (i.e., with particle and cell gas
masses being comparable) \enzo\ simulations typically displayed a much
higher level of gas structure.  This is unsurprising due to \enzo's
higher-order hydro solver.  Finally, \citet{2012ApJ...744...52P} show
the results of comparing \enzo\ in its non-AMR mode to a
smoothed-particle hydrodynamics code, SNSPH, in the context of
common-envelope binary stellar interactions.  The authors show that
the codes display reasonable convergence properties as a function of
simulation resolution, and also agree quite well with each other --
however, the observed mass-loss rates do not agree particularly well
with observations.

>>>>

Over the course of its existence, \enzo\ has been involved in numerous
comparisons with other astrophysical codes used for self-gravitating
fluid dynamics.  In general, \enzo\ behaves in a manner similar to other
grid-based (and particularly AMR-based) codes, as we will summarize below.

\enzo\ has been involved in multiple cosmological code comparisons,
including the Santa Barbara Cluster code comparison project
\citep{SantaBarbara}, a large comparison of N-body simulations
\citep{2008CS&D....1a5003H}, as well as several direct comparisons
between \enzo\ and the GADGET SPH code under a variety of
circumstances, including N-body and adiabatic hydrodynamics
\citep{2005ApJS..160....1O,2005MNRAS.364..909V, 2011MNRAS.418..960V}
and simulations of the Lyman-alpha forest \citep{2007MNRAS.374..196R}.
The \enzo\ code typically has a more difficult time resolving
small-scale self-gravitating structures (for an equivalent dark matter
particle count and nominally equivalent force resolution), but does
comparably well as a tree-based code for larger structure, and is
typically superior in terms of resolving fluid features due to its
higher-order (and artificial viscosity-free) Piecewise Parabolic
Method hydrodynamics solver.  When examining classical test cases such
as the Santa Barbara project \citep{SantaBarbara}, \enzo\ forms galaxy
clusters with very similar density, temperature, and entropy profiles
to other grid-based codes that use Godunov-type hydro methods, which
systematically differed from particle-based codes using SPH in this
code comparison.  Similarly, in galaxy cluster simulations that look
specifically at the properties of cosmological shocks
\citep[e.g.][]{2011MNRAS.418..960V}, \enzo\ produces results that are
similar to other high-order grid-based hydrodynamics codes, and far
superior performance of \enzo\ is observed (in terms of resolution of
fluid features and shock detection) in low-density regions when
compared to a particle-based code.  In tests of the Lyman-alpha forest
that include radiative cooling and a uniform metagalactic ultraviolet
background, \enzo\ and Gadget provide results on metrics such as the
matter power spectrum that are comparable to within 5\%
\citep{2007MNRAS.374..196R}.

Several comparisons have been made that focus specifically on
hydrodynamics solvers and fluid behavior.  In particular, the work of
\citet{2007MNRAS.380..963A} and \citet{Tasker2008} perform
head-to-head comparisons between several grid- and particle-based
codes for a variety of fluid-centric test problems (including shocked gas clouds,
self-gravitating, translating clouds, and Sedov-Taylor explosions),
and show that \enzo\ is comparable or superior in behavior to the
other grid-based hydrodynamics codes involved in the comparison, and
provide useful information on the sort of practical challenges that a
user of an
AMR code such as \enzo\ may experience.  More specific comparisons, including one
specifically testing the linear and nonlinear growth of the
Kelvin-Helmholz instability \citep{2012ApJS..201...18M}, as well as a
comparison that more
broadly examines Galilean invariance in grid-based codes
\citep{2010MNRAS.401.2463R}, show that \enzo, and in particular its
implementation of the Piecewise Parabolic Method hydrodynamics solver,
converge to the correct solution as expected, and generally provide
less diffusive solutions than lower-order codes, including those that
use artificial viscosity.  Finally, two code comparison projects have
been undertaken to examine turbulence in hydro codes -- one studied
the behavior of decaying isothermal supersonic turbulence
\citep{2009A&A...508..541K}, and the other looked at supersonic
magnetohydrodynamical turbulence \citep{2011ApJ...737...13K}.  Both
included the \enzo\ code, with the former testing the PPM
hydrodynamics and the latter the constrained transport MHD
implementation of \citet{Collins10}.  In both cases, \enzo\ performed similarly to other
grid-based codes that use Godunov-based fluid solvers, and typically
had better effective resolution than particle-based codes using the
same number of particles as the \enzo\ simulation used grid cells.

Three other comparisons between the \enzo\ code and other simulation
tools have been performed that focus on physics other than gravity and
fluid flow.  The flux-limited diffusion radiation transport scheme was
measured against several test problems by \citet{IlievEtAl2009},
producing results that are similar to both expected results (i.e.,
analytic test problems) and other methods (i.e., codes using other
methods, written by other groups), although there are some minor
differences (although all codes in the study exhibited differences
from the majority of other codes on at least a subset of the tests).
\citet{2011ApJ...726...55T} shows the results of varied reaction rate
coefficients for the formation of molecular hydrogen via the 3-body
process in both the \enzo\ and Gadget-2 codes.  Similar trends were
visible in both the \enzo\ and Gadget simulations, though at a
nominally equivalent resolution (i.e., with particle and cell gas
masses being comparable) \enzo\ simulations typically displayed a
substantially higher level of gas structure.  This is unsurprising due
to \enzo's higher-order hydro solver.  Finally,
\citet{2012ApJ...744...52P} show the results of comparing \enzo\ in
its non-AMR mode to a smoothed-particle hydrodynamics code, SNSPH, in
the context of common-envelope binary stellar interactions.  The
authors show that the codes display reasonable convergence properties
as a function of simulation resolution, and also agree quite well with
each other -- however, the observed mass-loss rates do not agree
particularly well with observations.
